Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-11-27 Moltres.tex
handles description of the model from ORNL.

\Cref{fig:temp_compare} shows a comparison between Moltres predicted temperature
profiles with cosinusoidal gamma heating and \gls{MSRE} design models
\cite{briggs_molten-salt_1964} in the hottest channel and adjacent graphite. The
profile shapes are in decent qualitative agreement with both Moltres and
\gls{MSRE} calculations showing a peak in graphite temperature before the
reactor outlet. Fuel temperature increases monotonically in both Moltres and
\gls{MSRE} models. In the \gls{MSRE} design, the moderator
temperature at the reactor inlet is about 20 degrees Fahrenheit larger than the
fuel temperature, whereas the temperatures are about the same in the Moltres
model. This difference is likely because the \gls{MSRE} design model 
neglected axial heat conduction \cite[p. 99]{briggs_molten-salt_1964}.

>>>>

\Cref{fig:temp_compare} shows a comparison between Moltres predicted temperature
profiles with cosinusoidal gamma heating and \gls{MSRE} design calculations
\cite{briggs_molten-salt_1964} in the hottest channel and adjacent graphite. 
The \gls{MSRE} design calculation in \cref{fig:temp_compare} was conducted in 
1963
32-group calculations using legacy computing tools (GAM-I, MODRIC, and 
EQUIPOSE, and THERMOS). That calculation was conducted in two-dimensional R-Z 
geometry (a cylinder with angular symmetry), with 20 spatial regions. Notably, 
one limitation of the \gls{ORNL} model was the control rod thimbles that, due to 
angular symmetry, were effectively a cylindrical shell of metal.

The profile shapes are in decent qualitative agreement with both Moltres and
\gls{MSRE} calculations, showing a peak in graphite temperature before the
reactor outlet. Fuel temperature increases monotonically in both Moltres and
\gls{MSRE} models. In the \gls{MSRE} design, the moderator
temperature at the reactor inlet is about 20 degrees Fahrenheit larger than the
fuel temperature, whereas the temperatures are about the same in the Moltres
model. This difference is likely because the \gls{MSRE} design model 
neglected axial heat conduction \cite[p. 99]{briggs_molten-salt_1964}.
